\input{settings.tex}

\begin{document}

\input{header.tex}

\secfont

\aboutMe{
I am an inquisitve Computer Engineering student with an affinity for programming and IoT. Throughout the duration of my course, I have found working on projects to automate and improve others' lives very rewarding. I am eager to continue my journey in IT and undertake training and gain experiences to advance my career.
}

\experience{Education}
{
    \entry{2018 - Today}{Student Computer Engineering | Rotterdam University of Applied Sciences}
    {
    I am currently a second year student. In my major, I am working on varied projects including IoT, electrical engineering and programming.
    }
    \entry{2015 - 2017}{Student Systems Administration | ITVitae Learning, Amersfoort}
    {
    I followed a study and working course to start employment as a systems administrator. Throughout my studies, I have learned a lot and worked with many open-source operating systems like Ubuntu Linux, RedHat Linux, Debian Linux and SUSE Linux.
    }
    \entryShort{2014 - 2015}{Student Molecular Science and Technology | TU Delft}
    \entryShort{2013 - 2014}{Student Computer Engineering | TU Delft}
    \entry{2006 - 2013}{VWO NG-NT | Lentiz Groen van Prinstererlyceum, Vlaardingen}
    {
    I took extra classes of Latin and Ancient Greek. I also followed extra English classes for an IB English A Language \& Literature HL certificate.
    }
}

\experience{Employment History}
{
    \entry{2019 - Today}{Teaching Assistant | Rotterdam University of Applied Sciences}
    {
    I help assist teachers teach during class. I also teach extracurricular to help overachieving students challenge themselves.
    }
    \entry{2015 - 2016}{Intern Systems Administration | Fox-IT, Delft}
    {
    I worked on an assignment involving optimizing and documenting Fox's internal JIRA-installation, and gave advice on how to better deploy their software stack in a closed-off network. I also worked on automatic deployment of new machines using Puppet.
    }
    \entry{2014 - 2017}{Volunteer | De Kroepoekfabriek, Vlaardingen}
    {
    I worked at the front of house to control the lights during a concert. I also helped at the bar to work as a service employee serving beverages.
    }
}

\skill{Skills}
{
    \entrySkill{Programming Languages}{Java, C++, Haskell, Kotlin}
    \entrySkill{Operating Systems}{Ubuntu, Debian, RedHat, SUSE, Windows Server}
    \entrySkill{Software}{MySQL, PostgreSQL, Puppet, JIRA, Apache, NGINX}
    \entrySkill{IoT}{AVR, Arduino}
    \entrySkill{Languages}{English, Dutch, Mandarin (learning)}
}

\vspace{1cm}

\contacts{Contact me}
{
    rolf@scales.blue & +31 6 28 62 41 73 & \href{https://www.linkedin.com/in/rolfdon/}{linkedin.com/in/rolfdon/} 
}

\end{document}
